Artin Group Presentations Arising from Cluster Algebras

### 2014-08-20 Paper.tex
Added Reference

\begin{def}\cite[Definition 4.1]{FT13}
Let $\Gamma$ be a diagram of affine type with n + 1 vertices. Then we define $W_{\Gamma}$ to be the diagram with generators $s_{1}, \dots, s_{n}$ and satisfying the following relations:
\begin{enumerate}
\item[(R1)] $s_{i}^{2} = e$ for all i = 1, \dots, n
\item[(R2)] $(s_{i}s_{j})^{m_{ij}} = e$ where 
$$m_{ij} = 
\begin{cases}
2 &\text{if there is no arrow between i and j in $\Gamma$} \\
3 &\text{if there is an arrow of weight 1 between i and j in $\Gamma$} \\
4 &\text{if there is an arrow of weight 2 between i and j in $\Gamma$} \\
6 &\text{if there is an arrow of weight 3 between i and j in $\Gamma$} \\
\infty &\text{otherwise}
\end{cases}$$
\item[R(3)] For every chordless oriented cycle:
$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
define for l $\in \{0, \dots, d-1\}$, 
$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
Then take the relation $(s_{i_{l}}p(i_{l}, i_{l+1}))^{m(l)} = e$ where
$$m(l) =
\begin{cases}
2 &\text{if $t(l)=0$} \\
3 &\text{if $t(l)=1$} \\
4 &\text{if $t(l)=2$} \\
6 &\text{if $t(l)=3$}
\end{cases}$$
\item[R(4)] For each subdiagram of $\Gamma$ of the form shown in the first column of \ref{table1}, we add the relation(s) listed in the second column.
\end{enumerate}
\end{def}

>>>>

\begin{def}\cite[Definition 4.1]{FT13}
Let $\Gamma$ be a diagram of affine type with n + 1 vertices. Then we define $W_{\Gamma}$ to be the diagram with generators $s_{1}, \dots, s_{n}$ and satisfying the following relations:
\begin{enumerate}
\item[(R1)] $s_{i}^{2} = e$ for all i = 1, \dots, n
\item[(R2)] $(s_{i}s_{j})^{m_{ij}} = e$ where 
$$m_{ij} = 
\begin{cases}
2 &\text{if there is no arrow between i and j in $\Gamma$} \\
3 &\text{if there is an arrow of weight 1 between i and j in $\Gamma$} \\
4 &\text{if there is an arrow of weight 2 between i and j in $\Gamma$} \\
6 &\text{if there is an arrow of weight 3 between i and j in $\Gamma$} \\
\infty &\text{otherwise}
\end{cases}$$
\item[(R3)] For every chordless oriented cycle:
$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
define for l $\in \{0, \dots, d-1\}$, 
$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
Then take the relation $(s_{i_{l}}p(i_{l}, i_{l+1}))^{m(l)} = e$ where
$$m(l) =
\begin{cases}
2 &\text{if $t(l)=0$} \\
3 &\text{if $t(l)=1$} \\
4 &\text{if $t(l)=2$} \\
6 &\text{if $t(l)=3$}
\end{cases}$$
\item[(R4)] For each subdiagram of $\Gamma$ of the form shown in the first column of \ref{table1}, we add the relation(s) listed in the second column.
\end{enumerate}
\end{def}
